---
title: "p8015_hw1_skh2164"
author: "Sarah Haberlack"
date: "2023-09-22"
output: 
 github_document
---
# Problem 1

```{r weather_df}
data("early_january_weather")
early_january_weather
```

The `early_january_weather` dataset describes meteorological conditions at every hour from January 1 to January 15, 2013 in Newark, NJ. It contains variables `origin, year, month, day, hour, temperature, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib,` and `time_hour`. We will primarily be looking at time, temperature and humidity. The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature of was `r mean(early_january_weather$temp)`. 

## Scatterplot
```{r}
library(tidyverse)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("weather_scatter.pdf")
```

The scatterplot shows Newark temperature and humidity level for the first 2 week of January. 
Over this two-week time period, the average daily temperature rises around 15 degrees. 
We can see that as humidity increases, the daily range of high and low temperatures become much smaller.

# Problem 2

## Create dataframe

```{r p2_df}
p2_df = 
  tibble(
    num_vec = rnorm(10),
    log_vec = num_vec > 0,
    char_vec = character(length = 10),
    factor_vec = factor(x = char_vec, 3)
  )
```

We will now try to take the means of each variable.
```{r}
mean(p2_df$num_vec)
mean(p2_df$log_vec)
mean(p2_df$char_vec)
mean(p2_df$factor_vec)
```

When we take the mean of the numerical vector `num_vec` and the logical vector `log_vec`, we get a numerical response--the command functions as intended. However, when we try to take the mean of the character vector `char_vec` and the factor vector `factor_vec`, we received the a warning message that `argument is not numeric or logical: returning NA`. 